A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-14 README.Rmd
removed current-dir-related check in Makefile update to README

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
```

@@

@@

**Note: Windows user need to hand edit the `Makefile` and set current_path to the current directory and use `make all DOCKER=TRUE WINDOWS=TRUE`. We hope that future releases of Docker for Windows will not require that workaround.**

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(readr)
library(pander)
```

@@

# Resources

```{r, include=FALSE}
resources <- read_csv(here("data", "resources.csv"), trim_ws = FALSE)
```

```{r, echo=FALSE, asis=TRUE}
pander(
  resources,
  split.tables = Inf,
  split.cells = Inf,
  missing = "",
  keep.line.breaks = TRUE,
  style = "multiline"
)
```

@@

**Note: Windows user need to manually edit the `Makefile` and set current_path to the current directory and use `make all DOCKER=TRUE WINDOWS=TRUE`. We hope that future releases of Docker for Windows will not require that workaround.**
